---
title: "Homework5"
author: "Yi Wang"
date: "Oct. 5th, 2018"
output: html_document
---

## Homework 5
*Question 1 Modify your function from the Problem 2 (Lab5 Activity). The function should simulate N rounds of the game (instead of just one) and return the proportion of times you win the bet. Run the function with N = 1000 and 10000.*
```{r}
win <- function(N, x = 0){
 for (i in 1:N) {
   s <- sample(1:6, 4, replace = T)
  for (j in 1:4) {
    if(s[j] == 6){
      x = x + 1
      break
    }
  }
   
 }
 return(x/N)
}

win(1000)
win(10000)


```
*Question 2 Write a function that will find the smallest element of a given vector (built-in min() is not allowed). Your function should return the smallest element and index of the smallest element. Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.*
```{r}
m <- function(a){
   s <- a[1]
  for (i in 1 : length(a)) {
   if(a[i] < s){
     s = a[i]
     x = c(s, i)
   } 
  }
   return(paste("The smallest element -", x[1],"and index is", x[2]))
}

m(c(2,3,4,1,3,51,0))
m(c(1, 4, 2, 0, 5))

```

```

